### 2023-02-12 paper-reviews/papers-2023.tex
Add DSP Derby article

    The article describes ARM 64-bit only architecture called Helios. It is a first licensable CPU that combines OOO and multithreaded execution. The main application for the processor are data transfer infrastructure and automotive industry. The processor architecture supports INT8 and FP16 formats that are the current trend for DNN acceleration. On top of INT8 and FP16 the processor can be closely integrated with various accelerators.
\end{itemize}

>>>>

    The article describes ARM 64-bit only architecture called Helios. It is a first licensable CPU that combines OOO and multithreaded execution. The main application for the processor are data transfer infrastructure and automotive industry. The processor architecture supports INT8 and FP16 formats that are the current trend for DNN acceleration. On top of INT8 and FP16 the processor can be closely integrated with various accelerators.

    \item \cite{Eyre:DSP-Derby:2001}:

    The article presents digital signal processor (DSP) design and development challenges. The author compares techniques used in DSPs with techniques typical for general-purpose processors. The article emphasizes DSP's requirement for predictable executing speed that is often more important than performance. The requirement is of course harder to fulfill with caches and out-of-order execution. VLIW, SIMD and highly compressed encodings are mentioned as an example of techniques prevailing in DPSs. There is also performance comparison of some DSPs with a superscalar processor that is based on FFT and FIR filter benchmarks.
\end{itemize}
